---
title: "Activity 2 - Day 1"
output: github_document
---

```{setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")

```

Question 1:
Is this an observational study or an experiment?

Answer:
This is an observational study as it summarizes the idea of freedom using multiple variables for different countries around the globe without trying to prove or justify an objective.

```{r}
ggplot(hfi, aes(x = pf_score)) +
  geom_histogram() + 
  labs(title = "Distribution of pf_score",
       x = "pf_score")
```

Question 2:
Describe the distribution of pf_score Is the distribution skewed? Are there any other interesting/odd features (outliers, multiple peaks, etc.)? What does that tell you about countries’ personal freedoms? Is this what you expected to see? Why, or why not?

Answer:
The distribution is skewed to the right making it the right skewed data. There are few outliers and multiple peaks present in the histogram generated. This is not what I expected to see. Since having an histogram 

```{r, warning = FALSE}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```
```{r, warning= FALSE}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

```{r}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```

```{r}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

```{r}

# review any visual patterns
hfi %>% 
  select(pf_score, pf_expression_influence, pf_expression_control) %>% 
  ggpairs()

#fit the mlr model
m_pf <- lm(pf_score ~ pf_expression_influence + pf_expression_control, data = hfi)
tidy(m_pf)
```

```{r}

summary(m_pf)
```

```{r}

glance(m_pf)
```

```{r}

# obtain fitted values and residuals
m_pf_aug <- augment(m_pf)

# plot fitted values and residuals
ggplot(data = m_pf_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```

```{r}

ggplot(data = m_pf_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

```{r}

hfi %>% 
  filter(countries == "United States" & year == 2016) %>% 
  select(pf_score, pf_expression_influence, pf_expression_control)
```

```{r}

hfi %>% 
  filter(countries == "United States" & year == 2016) %>% 
  predict(m_pf, .)
```

