---
title: "Activity 2 - Day 1"
output: github_document
---

```{setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")

```

Question 1:
Is this an observational study or an experiment?

Answer:
This is an observational study as it summarizes the idea of freedom using multiple variables for different countries around the globe without trying to prove or justify an objective.

```{r}
ggplot(hfi, aes(x = pf_score)) +
  geom_histogram() + 
  labs(title = "Distribution of pf_score",
       x = "pf_score")
```

Question 2:
Describe the distribution of pf_score Is the distribution skewed? Are there any other interesting/odd features (outliers, multiple peaks, etc.)? What does that tell you about countries’ personal freedoms? Is this what you expected to see? Why, or why not?

Answer:
The distribution is skewed to the right making it the right skewed data. There are few outliers and multiple peaks present in the histogram generated. This is not what I expected to see. Since having an histogram 

```{r, warning = FALSE}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```
```{r, warning= FALSE}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

```{r}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```

```{r}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

